### 2017-08-03 Paper01_EnthalpyAndCrystallization.tex
Fragility - replaced word with glossy terms

\subsubsection{Fragility}

Using the isochronic \acrshort{dsc} data the fragility of the \MgZnCa~ system could be established for both the bulk and film. Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.

@@

Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid Fragility parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.

The fragility $m$ could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.

@@

For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$. For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$. See Figure \ref{fig:Fragility_BulkFilm_mValue}.

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Fragility_BulkFilm_mValue}
\end{figure}

>>>>

\subsubsection{\Acrlong{m}}

Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film. Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.

@@

Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid \acrlong{m} parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.

The \gls{m} could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.

@@

For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$, giving a $D^{*}=20.4$, and a \acrlong{m} $m=44.9$. For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.861$, giving a $D^{*}=10.0$, and \acrlong{m} $m=75.0$. See Figure \ref{fig:Fragility_BulkFilm_mValue}.

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
	\caption[Table of contents Capition]{Fitted \acrfull{m} for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Fragility_BulkFilm_mValue}
\end{figure}
